---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# UnsupLP1

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/ChrisKeefe/UnsupLP1.svg?branch=master)](https://travis-ci.com/ChrisKeefe/UnsupLP1)
<!-- badges: end -->

UnsupLP1 is a sample package written for CS599 - Unsupervised Learning, which demonstrates my ability to:

- build an R package
- implement, run, and test functions in R related to Unsupervised Learning
- set up Travis for CI checks on each commit
- Adequately document a package to allow reasonable ease of use

## Installation

You can install a development version of this package from [GitHub](https://github.com/ChrisKeefe/UnsupLP1) with:

``` r
# install.packages("devtools")
devtools::install_github("ChrisKeefe/UnsupLP1")
```
## Usage

Here are some basic examples of how to use the functions in this package. For 
more complete usage information, please see the function documentation.

```{r example}
library(UnsupLP1)
## basic example code
# Cluster the iris data set into three clusters:
KMEANS(iris[1:4], K=3)

# Split a data matrix into 80% TRAIN and 20% TEST
split_train_and_test(iris, train.prop=0.8, test.prop=0.2)
```
